### 2012-04-06 doc/theses/mikula/conclusion.tex
Master thesis: Corrections and final(?) additions.

Finally, we proposed a simple way how to combine the inferred statements with existing grammar inferring methods of the XML schema inference and we implemented it using the jInfer framework. Thus, we created the first complete, ready-to-use, and extensible implementation of the XML xchema inference exploiting XQuery queries besides XML data.

\todo[inline]{Nejake prehladne zhrnutie plusov a minusov? ANO}

\section{Future Work}
This work implements only some ideas discussed in the overview in Chapter \ref{CHAPTER_analysis_of_xquery}, leaving most of them for future work. Also, the implemented algorithms can be further refined as was already mentioned in Chapter \ref{CHAPTER_proposed_algorithm} with the presentation of the algorithms. For example thorough processing of user-defined function calls.

>>>>

Finally, we proposed a simple way how to combine the inferred statements with existing grammar inferring methods of the XML schema inference and we implemented it using the jInfer framework. Thus, we created the first complete, ready-to-use, and extensible implementation of the XML schema inference exploiting XQuery queries besides XML data.

As the main advantages and disadvantages of the work we list the following.
\begin{itemize}
\renewcommand{\labelitemi}{$+$}
\item Elaboration of the overview how XQuery queries can help in the process of XML schema inference.
\item Incorporation of the lexical and syntax analyses of input queries creating their syntax trees.
\item Development of the static type analysis including PathTypes, which can be easily extended and use in possible future extensions.
\item Extension of the existing method of key discovery, achieving better results.
\item Our implementation using the jInfer framework is the first implementation of XML schema inference method utilizing XML operations.
\renewcommand{\labelitemi}{$-$}
\item In the proposed algorithm we dealt with a small part of possible refinements discussed in the overview.
\item The combination with existing methods of inference is done in the simplest way, not modifying the grammar rules. But, from the view of recent XML schema inference research, the modification of the grammar rules according to the statements inferred from XML operations is vastly interesting.
\item Since large real-world sets of XQuery queries are not available, we did not perform experiments using such sets. We only tested our method using a relatively small number input of queries, decreasing the level of reliability of the experimental results.
\end{itemize}

\section{Future Work}
As already mentioned, this work implements only some ideas discussed in the overview in Chapter \ref{CHAPTER_analysis_of_xquery}, leaving most of them for future work. Also, the implemented algorithms can be further refined as was already mentioned in Chapter \ref{CHAPTER_proposed_algorithm} with the presentation of the algorithms. For example thorough processing of user-defined function calls.

### 2012-04-06 doc/theses/mikula/proposed_algorithm.tex
Master thesis: Corrections and final(?) additions.

\section{Overview}
\begin{figure}
\includegraphics[scale=1]{algorithm.eps}
\caption{Steps of the proposed algorithm.}
\label{FIG_steps_algorithm}
\end{figure}

@@

\begin{enumerate}
\item \textbf{Construction of a syntax tree}. We use lexical and syntax analyses proposed in \cite{thesis_schejbal} and for each XQuery on input, we construct a data structure defined in Definition \ref{DEF_syntax_tree}.
\item \textbf{Static Analysis of expression types}. The algorithm searches for expressions in the syntax trees and statically (without evaluation) determines their types. \todo{Co se mysli? Datove typy?}
\item \textbf{Inference of built-in types}. When the types of expressions are determined, selected forms of expression are utilized to infer types of elements and attributes.
\item \textbf{Key discovery}. The final step is an extension of approach \cite{Necasky:2009:DXK:1529282.1529414} inferring keys and foreign keys.
\end{enumerate}

@@

\begin{figure}
\includegraphics[scale=0.6]{syntax_tree_1.eps}
\caption{Sample syntax tree 1.}
\label{FIG_syntax_tree_1}
\end{figure}

@@

\subsection{Expression Types}
\begin{figure}
\caption{XSD built-in atomic types.}
\label{FIG_xsd_built_in_atomic_types}
\includegraphics[scale=0.65]{xsd-types.eps}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.5]{syntax_tree_1_types.eps}
\caption{Sample syntax tree 1 after the static analysis of types.}
\label{FIG_syntax_tree_1_types}
\end{figure}

@@

\section{Step 3: Inference of Built-in Types}
\todo[inline]{Rekurzia sa nevnara do FunctionBodyNodes a PathExprNodes - napisat, alebo je to detail?}
In this step, the algorithm goes through the syntax tree to infer types of elements and attributes from expressions using the type information from the previous step. These two steps could be merged together but for better comprehension we present it separately.

@@

@@

\begin{figure}
\includegraphics[scale=1]{syntax_tree_1_types_type_inference.eps}
\caption{Example of an inference of a type from a function call.}
\label{FIG_syntax_tree_1_types_type_inference}
\end{figure}

@@

\subsection{Example}
\begin{figure}
\includegraphics[scale=0.7]{syntax_tree_2.eps}
\caption{Sample syntax tree 2.}
\label{FIG_syntax_tree_2}
\end{figure}

>>>>

\section{Overview}
\begin{figure}
\includegraphics[scale=1]{algorithm.eps}
\caption{Steps of the proposed algorithm}
\label{FIG_steps_algorithm}
\end{figure}

@@

\begin{enumerate}
\item \textbf{Construction of a syntax tree}. We use lexical and syntax analyses proposed in \cite{thesis_schejbal} and for each XQuery on input, we construct a data structure defined in Definition \ref{DEF_syntax_tree}.
\item \textbf{Static Analysis of expression types}. The algorithm searches for expressions in the syntax trees and statically (without evaluation) determines their types. See Section \ref{SECTION_expression_types}.
\item \textbf{Inference of built-in types}. When the types of expressions are determined, selected forms of expression are utilized to infer types of elements and attributes.
\item \textbf{Key discovery}. The final step is an extension of approach \cite{Necasky:2009:DXK:1529282.1529414} inferring keys and foreign keys.
\end{enumerate}

@@

\begin{figure}
\includegraphics[scale=0.6]{syntax_tree_1.eps}
\caption{Sample syntax tree 1}
\label{FIG_syntax_tree_1}
\end{figure}

@@

\subsection{Expression Types} \label{SECTION_expression_types}
\begin{figure}
\caption{XSD built-in atomic types}
\label{FIG_xsd_built_in_atomic_types}
\includegraphics[scale=0.65]{xsd-types.eps}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.5]{syntax_tree_1_types.eps}
\caption{Sample syntax tree 1 after the static analysis of types}
\label{FIG_syntax_tree_1_types}
\end{figure}

@@

\section{Step 3: Inference of Built-in Types}
In this step, the algorithm goes through the syntax tree to infer types of elements and attributes from expressions using the type information from the previous step. These two steps could be merged together but for better comprehension we present it separately.

@@

Likewise the previous step, the syntax tree is recursively searched for expressions meeting the conditions for the type inference. A little difference is that the recursion stops at \texttt{FunctionsBodyNode} and \texttt{PathExprNode} nodes, because the processing of these nodes requires a different approach, which we do not deal with in this thesis.

@@

\begin{figure}
\includegraphics[scale=1]{syntax_tree_1_types_type_inference.eps}
\caption{Example of an inference of a type from a function call}
\label{FIG_syntax_tree_1_types_type_inference}
\end{figure}

@@

\subsection{Example}
\begin{figure}
\includegraphics[scale=0.7]{syntax_tree_2.eps}
\caption{Sample syntax tree 2}
\label{FIG_syntax_tree_2}
\end{figure}
